Trans-Dimensional Bayesian Inference for Gravitational Lens Substructures

### 2015-07-23 Papers/ms.tex
A few more words

The joint posterior distribution for the SIE mass total substructure mass
for the Cosmic Horseshoe is given in Figure~\ref{fig:masses2}. As with
the simulated data (Figure~\ref{fig:masses}), we see an expected negative
correlation between these two quantities. However, the points are not as
smoothly distributed in this case (we discuss this issue further
in Section~\ref{sec:convergence}). An upper ``limit'' on the SIE mass, with
95\% posterior probability, is $5.21 \pm 0.02\times 10^{12} M_\odot$
The posterior distribution for
$N_{\rm lens}$ (Figure~\ref{fig:N_lens2})
also shows some evidence for more than zero substructures.
In particular, the prior probability for $N_{\rm lens} > 0$ was 10/11
$\approx$ 0.91, whereas the posterior probability is approximately 0.97.
This corresponds to a Bayes Factor of approximately 3 in favour of
$N_{\rm lens} > 0$ versus the alternative $N_{\rm lens} = 0$.

@@

As with any inference, the results presented here may be sensitive to many of
the input modelling assumptions, and a slightly different (yet still
``reasonable'') set of choices might yield different results. For example, if
the density profile of the lens was smooth but not of the SIE form, and the
data were informative enough to show this, the current
model would only be able to explain the data by adding substructures. Hence, an alternative explanation for these results is that, rather than containing a substructure, the density profile of the lens is simply not within
the SIE family. One way of further investigating this is to use a different family of
smooth lens models and doing model selection based on the marginal likelihoods.
Another option which we defer to future work is to implement a more flexible
model (such as a concentric mixture of concentric elliptical lenses). This
result is consistent with that of \citet{2008MNRAS.388..384D}, who found a slight preference for an elliptical power law profile over the SIE
(which is a specific case of an elliptical power law).

>>>>

The joint posterior distribution for the SIE mass total substructure mass
for the Cosmic Horseshoe is given in Figure~\ref{fig:masses2}. As with
the simulated data (Figure~\ref{fig:masses}), we see an expected negative
correlation between these two quantities. However, the points are not as
smoothly distributed in this case (we discuss this issue further
in Section~\ref{sec:convergence}). An upper ``limit'' on the SIE mass, with
95\% posterior probability, is $5.21 M_\odot$.
The posterior distribution for
$N_{\rm lens}$ (Figure~\ref{fig:N_lens2})
also shows some evidence for more than zero substructures.
In particular, the prior probability for $N_{\rm lens} > 0$ was 10/11
$\approx$ 0.91, whereas the posterior probability is approximately 0.97.
This corresponds to a Bayes Factor of approximately 3 in favour of
$N_{\rm lens} > 0$ versus the alternative $N_{\rm lens} = 0$.

@@

As with any inference, the results presented here may be sensitive to many of
the input modelling assumptions, and a slightly different (yet still
``reasonable'') set of choices might yield different results. For example, if
the density profile of the lens was smooth but not of the SIE form, and the
data were informative enough to show this, the current
model would only be able to explain the data by adding substructures. Hence, an alternative explanation for these results is that, rather than containing a substructure, the density profile of the lens is simply not within the SIE$+\gamma$ family. In fact, some of the posterior
samples obtained contain massive substructures outside of the image, which
could be modelling higher-order effects of the environment beyond what is
captured by the simple external shear model.
One way of further investigating this is to use a different family of
smooth lens models and doing model selection based on the marginal likelihoods.
Another option which we defer to future work is to implement a more flexible
model (such as a concentric mixture of concentric elliptical lenses). This
result is consistent with that of \citet{2008MNRAS.388..384D}, who found a slight preference for an elliptical power law profile over the SIE
(which is a specific case of an elliptical power law).
